Improving credibility and efficiency of decision-making \\ within democratic communities via a statistical quorum

### 2018-04-19 statistical-quorum.tex
Data.

Users on PeerMind made 139 proposals over the span of a semester (this figure
excludes proposals that were withdrawn before voting began).
Out of those 139 proposals, 98 proposals passed. In comparison, 70 out of 73 proposals passed
in the semester prior.

PeerMind users made 3958 votes, whereas 1396 votes were made during spring semester.
Even after adjusting for the larger number of proposals made in the fall, participation
increased significantly.
From around 19 votes per proposal to 28 votes per proposal, on average.

Plotting time spent per user on PeerMind gives further insights into the democratization of decision-making. While the average person spent 7002 seconds on the application, the distribution of users is fairly long-tailed with many people only spending 30 minutes and some people spending upwards of 20 hours. We believe many people who only spent 30 minutes would not participate in the offline council at all (which is confirmed by much lower attendance and fewer votes). Furthermore, people who need more time to discuss are given the freedom to do so without wasting time of those who are not interested in the pertinent discussion.

@@

>>>>

Members on PeerMind made 139 proposals over the span of a semester (this figure
excludes proposals that were withdrawn before voting began).
Out of those 139 proposals, 98 proposals passed. In comparison, 70 out of 73 proposals passed
in the semester prior.

PeerMind users made 3958 votes, whereas 1396 votes were made during spring semester.
Even after adjusting for the larger number of proposals made in the fall, voting participation
increased significantly.
From around 19 votes per proposal in the spring to 28 votes per proposal in the fall, on average.
(Not everyone present at a council has to vote.)

@@

Plotting time spent per community member on PeerMind gives insights into the
democratization of decision-making. While the average person spent 7002 seconds on the application, the distribution of users is fairly long-tailed with many people only spending 30 minutes and some people spending upwards of 20 hours. We believe many people who only spent 30 minutes would not participate in the offline council at all (which is confirmed by much lower attendance and fewer votes). Furthermore, people who need more time to discuss are given the freedom to do so without wasting time of those who are not interested in the pertinent discussion.
